Report: Complex Support Vector Detector for Large MIMO System

### 2015-10-12 Report Aug 5 2015/Report Aug 2015.tex
Report revised stopping cirteria

@@

Condition in (\ref{original KKT condition3}) is called KKT complementary condition, the value of $\sum_{i=1}^{L}\bar{a}_{i}c_{i}(\bar{\mathbf{w}})$ can be used to monitor how close the solution is to the global optimum. Thus it can be used as a stopping criterion. In the constraint optimization problem of (\ref{lagrange duality1}), the KKT complementary conditions are given by 
\begin{IEEEeqnarray}[\relax]{l}
\left\{\begin{array}{cc}
\alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})=0, i=1,2\cdots L\\
\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})=0, i=1,2\cdots L
\end{array}\right. 
\label{KKT complimentary}
\end{IEEEeqnarray}

@@

Where $\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
\Re{(\mathbf{K})}_{SS}& \Re{(\mathbf{K})}_{SN}\\
\Re{(\mathbf{K})}_{NS}& \Re{(\mathbf{K})}_{NN}
\end{IEEEeqnarraybox*}\right]$ is a permutation of $\Re{(\mathbf{K})}$, where $\Re{(\mathbf{K})_{SN}}$ denotes the sub matrix that consist of rows corresponding to set $S$ and columns corresponding to $N$, Notice that $\Re{(\mathbf{K})}_{SN}=\Re{(\mathbf{K})}_{NS}$, therefore, (\ref{real part decomposition inter1}) can be rewritten as 
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
\max_{\mathbf{a}, \mathbf{\hat{a}}}\quad \theta^{r}=-\frac{1}{2}[(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})+2(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})^{T}\Re{(\mathbf{K})}_{NS}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})]
+\Re{(\mathbf{y}_{S}^{T})}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})-\\
\nonumber
\epsilon(\mathbf{e}^{T}(\mathbf{a}_{S}+\hat{\mathbf{a}}_{S}))
-\frac{1}{2}(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\Re{(\mathbf{K})}_{NN}(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})+\Re{(\mathbf{y}_{N}^{T})}(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})-\epsilon(\mathbf{e}^{T}(\mathbf{a}_{N}+\mathbf{\hat{a}}_{N}))\\\nonumber+C(\mathbf{e}^{T}(\mathbf{R}^{r}),
\\
\left\{\begin{array}{ll}
0\leq [\mathbf{a}]_{i}([\hat{\mathbf{a}}]_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, N_{r}\\
\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, N_{r}\\
\end{array}\right.
\label{real part decomposition}
\end{IEEEeqnarray}
In each iteration, in (\ref{real part decomposition}), $\mathbf{a}_{N}$ is fixed and only the sub  QP problem that related to $\mathbf{a}_{S}$ is solved i.e 
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
\max_{\mathbf{a}_{S}, \mathbf{\hat{a}}_{S}}\quad \theta_{S}^{r}=-\frac{1}{2}[(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})]+[Re(\mathbf{y}_{S}^{T})-(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})^{T}\mathbf{K}_{NS}^{r}
](\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})-\\\nonumber\epsilon<\mathbf{e}^{T}, (\mathbf{a}_{S}+\mathbf{\hat{a}}_{S})>,
\\
\left\{\begin{array}{ll}
0\leq [\mathbf{a}_{S}]_{i}([\hat{\mathbf{a}}_{S}]_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i\in S\\
\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i\in S\\
\end{array}\right.
\label{subset optimization}
\end{IEEEeqnarray}
A proper work set selection strategy is required so that speed and performance requirement can be guaranteed. One idea is to perform update to dual variables that violate the complementary KKT conditions, which, based on (\ref{original KKT condition3}) in \ref{section lagrange duality}, can be formulated as 
\begin{IEEEeqnarray}[\relax]{l}
\left\{\begin{array}{ll}
(C\tilde{R}(\xi_{i}^{r})-\alpha_{i})\xi_{i}^{r}=0, i=1,2,\ldots, L\\
(C\tilde{R}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i})\hat{\xi}_{i}^{r}=0, i=1,2,\ldots, L\\
\alpha(\epsilon+\xi_{i}^{r}-\Re{(\mathbf{y}_{i})}+<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})=0, i=1,2,\ldots, L\\
\hat{\alpha}_{i}(\epsilon+\hat{\xi}_{i}^{r}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}+\Re{(\mathbf{y}_{i})})=0, i=1,2,\ldots, L\\
\end{array}\right.
\label{complementary KKT condition1}
\end{IEEEeqnarray}
According to Osuna's theorem\cite{osuna1997improved}, the final convergence can be guaranteed. In SMO algorithm, heuristic methods are used to find a work set of size two in order to accelerate the decomposition process\cite{platt1999fast}. The heuristic method first searches among the non-bound variables (that is $0<\alpha_{i}<C\tilde{R}(\xi^{r}_{i})$ and $0<\hat{\alpha}_{i}<C\tilde{R}(\hat{\xi}_{i})$), which are more likely to violate the complementary KKT conditions, Then searching the whole dual variable set. The second dual variable that can maximize optimization step size is chosen. An approximate step size is used as evaluator for sake of reducing computational cost.

Another idea for work set selection is to choose the dual variables whose update can provide the maximum improvements to dual objective function. That is

@@

where $\Delta_{S}=\mathbf{a}_{S}^{new}-\mathbf{a}_{S}$, $\mathbf{a}_{S}$ is the update of $\mathbf{a}^{new}_{S}$. $\bigtriangledown \theta_{S}^{r}$ in (\ref{maximum gain work set selection}),  based on (\ref{subset optimization}), can be written as 

@@

\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}[(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\mathfrak{n}_{S}-\hat{\Delta}_{S})+2(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta})_{S}]+[\Re{(\mathbf{y}^{T}_{S})}-(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\Re{(\mathbf{K})}_{NS}](\Delta_{S}-\hat{\Delta}_{S})\\
-\epsilon\mathbf{e}^{T}_{S}(\Delta_{S}+\hat{\Delta}_{S})=-\frac{1}{2}\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+[\Re{(\mathbf{y}^{T}_{S})}-(\mathbf{a}-\hat{\mathbf{a}})^{T}\Re{(\mathbf{K})}_{S}](\Delta_{S}-\hat{\Delta}_{S})\\

@@

Notice in (\ref{gain work set selection1}), we use 

@@

where $\Re{(\mathbf{K})}_{S}\in \mathbb{R}^{N_{r}\times S}$ denotes the matrix constructed by all the columns corresponding to the work set $S$. Then we define intermediate variable vector $\Phi\in \mathbb{C}^{N_{r}}$, $\Re{(\Phi)}=\Re{(\mathbf{y})}-\Re{(\mathbf{K})}(\mathbf{a}-\hat{\mathbf{a}})$ and $\Im{(\Phi)}=\Im{(\mathbf{y})}-\Re{(\mathbf{K})}(\mathbf{b}-\hat{\mathbf{b}})$
Thus (\ref{gain work set selection1}) can be rewritten as 

@@

\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}(\Delta_{S}-\hat{\Delta})^{T}_{S}\Re{(\mathbf{K})}_{SS}(\Delta-\hat{\Delta})_{S}+(\Re{(\Phi)}_{S})^{T}(\Delta-\hat{\Delta})_{S}-\epsilon\mathbf{e}^{T}_{S}(\Delta+\hat{\Delta})_{S}

@@

(C\tilde{R}(\xi_{i}^{r})-\alpha_{i})\xi_{i}^{r}=0, i=1,2,\ldots, L\\

@@

(C\tilde{R}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i})\hat{\xi}_{i}^{r}=0, i=1,2,\ldots, L\\

@@

\alpha(\epsilon+\xi_{i}^{r}-\Re{(\mathbf{y}_{i})}+<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})=0, i=1,2,\ldots, L\\

@@

\hat{\alpha}_{i}(\epsilon+\hat{\xi}_{i}^{r}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}+\Re{(\mathbf{y}_{i})})=0, i=1,2,\ldots, L\\\nonumber

@@

notice that in (\ref{KKT complementary3}) and (\ref{KKT complementary4}), there is at least one of $\epsilon+\xi_{i}^{r}-\Re{(\mathbf{y}_{i})}+<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}$ and  $\epsilon+\hat{\xi}_{i}^{r}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}+\Re{(\mathbf{y}_{i})}$ can be non zero, therefore in order to satisfy the equalities, at least one of $\alpha_{i}$ and $\hat{\alpha}_{i}$ need to be zero, that is $\alpha_{i}\hat{\alpha}_{i}=0$, because $0\leq \alpha_{i}(\hat{\alpha}_{i})\leq C\tilde{R}(\xi_{i}^{r})(C\tilde{R}(\hat{\xi}_{i}^{r}))$ and $\alpha_{i}\hat{\alpha}_{i}=0$, there is at least one of $C\tilde{R}(\xi_{i}^{r})-\alpha_{i}$ and $C\tilde{R}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i}$ in (\ref{KKT complementary1}) and (\ref{KKT complementary2}) is non zero, in order to satisfy the equalities, there is at least one of $\xi_{i}$ and $\hat{\xi}_{i}$ need to be zero, that is $\xi_{i}^{r}\hat{\xi}_{i}^{r}=0$. Hence we can substitute $\lambda_{i}=\alpha_{i}-\hat{\alpha}_{i}$ and $|\lambda_{i}|=\alpha_{i}+\hat{\alpha}_{i}$, therefore the update unit is the single optimization variable $\lambda_{i}$ rather than the pair $\alpha_{i}$ and $\hat{\alpha}_{i}$.

@@

\begin{IEEEeqnarray}[\relax]{l}
\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}\Sigma^{T}_{S}\Re{(\mathbf{K})}_{SS}\Sigma_{S}+(\Phi^{r}_{S})^{T}\Sigma_{S}-\epsilon<\mathbf{e}^{T}_{S},|\Lambda^{new}_{S}|-|\Lambda_{S}|>,
\label{gain work set selection lambda}
\end{IEEEeqnarray} 
In 1-D solver, $|S|=1$, the sub dual objective function corresponding to $\lambda_{m}$, $m=1,2,\ldots, N_{r}$ can be written as
\begin{IEEEeqnarray}[\relax]{l}
 \max_{\lambda_{m}}\quad \theta_{m}^{r}=-\frac{1}{2}(\lambda_{m}^{new})^{2}\Re{(\mathbf{K})}_{mm}
+[\Re{(\mathbf{y}_{m})}-\sum_{j\neq m}^{N_{r}}\Re{(\mathbf{K})}_{mj}\lambda_{j}]\lambda_{m}^{new}-\epsilon(|\lambda^{new}_{m}|),
 \label{optimization function 1-D}
 \end{IEEEeqnarray}
 Based on the definition of $\Phi$ in (\ref{gain work set selection2}), $\Re{(\Phi)}_{i}=\Re{(\mathbf{y}_{i})}-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\Re{(\mathbf{K})}_{ij}$, similarly, as to dual variable $\lambda^{i}_{i}$, $\Re{(\Phi)}_{i}^{i}=Im(y_{i})-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Re{(\mathbf{K})}_{ij}$. Thereafter, for sake of brevity, we use $\lambda_{i}$ instead of $\lambda_{i}^{r}$.
Take the partial derivative of $\theta_{m}^{r}$ respect to $\tilde{\lambda}^{new}_{m}$,  we have 
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
\frac{\partial \theta_{m}^{r}}{\partial \tilde{\lambda}^{new}_{m}}=-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}+\Re{(\mathbf{y}_{m})}-\sum_{j\neq m}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{mj}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))=\\
\nonumber
-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}+\Re{(\Phi)}_{m}+\lambda_{m}\Re{(\mathbf{K})}_{mm}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))\\
\Rightarrow \tilde{\lambda}_{m}^{new}=\lambda_{m}+\frac{\Re{(\Phi)}_{m}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))}{\Re{(\mathbf{K})}_{mm}},
\label{partial optimization function 1-D lambda}
\end{IEEEeqnarray}

 The update of $\alpha_{1}$ or $\hat{\alpha}_{1}$ is completed by clipping
\begin{IEEEeqnarray}[\relax]{l}
\lambda^{new}_{m}=[\tilde{\lambda}^{new}_{m}]^{CR^{'}(\xi_{m})}_{-CR^{'}(\xi_{m})}
\label{clipped new dual variable}
\end{IEEEeqnarray}

@@

based on (\ref{gain work set selection lambda}), The maximum gain of objective function respect to the $m$th optimization variable $\lambda_{m}$ is 

@@

In 1-D searching procedure, the optimization variable whose update has the maximum gain of sub dual objective function is chosen, assume the $k$th optimization variable is chosen, that is 

@@

k=\arg\max_{(m=1,2,\ldots, N_{r})} \bigtriangledown \theta_{m}^{r},

@@

R(\xi)=\frac{1}{2}\xi^{2},

>>>>

In $\epsilon$-SVR, the objective to exploit slack variables $\xi_{i}$ and $\hat{\xi}_{i}$ is to compensate the influences from the outliers that exceed the $\epsilon$-tube which are caused by noise.
Therefore in $\epsilon$-SVR, $\xi_{i}$ and $\hat{\xi}$ are defined as  
\label{definition of slack variable1}
\xi_{i}=\max(0, \mathbf{y}_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon)\\
\label{definition of slack variable2}
\hat{\xi}_{i}=\max(0, \mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-\mathbf{y}_{i}-\epsilon)
Because the distance of the estimations $\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b$ and the observation $\mathbf{y}_{i}$ can only exceeds the $\epsilon$-tube in one direction, therefore there is at most one of $\xi_{i}$ and $\hat{\xi}_{i}$ can be non zero. That is $\xi_{i}\hat{\xi}_{i}=0$.

@@

Condition in (\ref{original KKT condition3}) is called KKT complementary condition, the value of $\sum_{i=1}^{L}\bar{a}_{i}c_{i}(\bar{\mathbf{w}})$ can be used to monitor how close the solution is to the global optimum. Thus it can be used as a stopping criterion. In the constraint optimization problem of (\ref{lagrange duality1}), the KKT complementary conditions are given by 
\begin{IEEEeqnarray}[\relax]{l}
\left\{\begin{array}{cc}
\alpha_{i}(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})=0, i=1,2\cdots L\\
\hat{\alpha}_{i}(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})=0, i=1,2\cdots L
\end{array}\right. 
\label{KKT complimentary}
\end{IEEEeqnarray}
Based on the definitions of slack variables in (\ref{definition of slack variable1}) an (\ref{definition of slack variable2}), only when there is a outlier exists, $\xi_{i}$ or $\hat{\xi}_{i}$ can be non zero, that is 
\begin{equation}
\xi_{i}(\hat{\xi}_{i})=|\mathbf{y}_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})|_{\epsilon},
\label{definition of slack variable3}
\end{equation} 
because the distance of the estimation $\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b$ and the observation $\mathbf{y}_{i}$ can only exceeds the $\epsilon$-tube in one direction, as shown in Fig. \ref{epsilon-SVR}. Therefore at most one of $(y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})$  and $(\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})$ can be zero. In order to satisfy the KKT complementary conditions in (\ref{KKT complimentary}), at least one of $\alpha_{i}$ and $\hat{\alpha}_{i}$ need to be zero, that is $\alpha_{i}\hat{\alpha}_{i}=0$.

@@

Where $\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
\Re{(\mathbf{K})}_{SS}& \Re{(\mathbf{K})}_{SN}\\
\Re{(\mathbf{K})}_{NS}& \Re{(\mathbf{K})}_{NN}
\end{IEEEeqnarraybox*}\right]$ is a permutation of $\Re{(\mathbf{K})}$, where $\Re{(\mathbf{K})_{SN}}$ denotes the sub matrix that consist of rows corresponding to set $S$ and columns corresponding to $N$, Notice that $\Re{(\mathbf{K})}_{SN}=\Re{(\mathbf{K})}_{NS}$, therefore, (\ref{real part decomposition inter1}) can be rewritten as 
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
\max_{\mathbf{a}, \mathbf{\hat{a}}}\quad \theta^{r}=-\frac{1}{2}[(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})+2(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})^{T}\Re{(\mathbf{K})}_{NS}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})]
+\Re{(\mathbf{y}_{S}^{T})}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})-\\
\nonumber
\epsilon(\mathbf{e}^{T}(\mathbf{a}_{S}+\hat{\mathbf{a}}_{S}))
-\frac{1}{2}(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\Re{(\mathbf{K})}_{NN}(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})+\Re{(\mathbf{y}_{N}^{T})}(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})-\epsilon(\mathbf{e}^{T}(\mathbf{a}_{N}+\mathbf{\hat{a}}_{N}))\\\nonumber+C(\mathbf{e}^{T}(\mathbf{R}^{r}),
\\
\left\{\begin{array}{ll}
0\leq [\mathbf{a}]_{i}([\hat{\mathbf{a}}]_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i=1,2,\ldots, N_{r}\\
\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i=1,2,\ldots, N_{r}\\
\end{array}\right.
\label{real part decomposition}
\end{IEEEeqnarray}
In each iteration, in (\ref{real part decomposition}), $\mathbf{a}_{N}$ is fixed and only the sub  QP problem that related to $\mathbf{a}_{S}$ is solved i.e 
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
\max_{\mathbf{a}_{S}, \mathbf{\hat{a}}_{S}}\quad \theta_{S}^{r}=-\frac{1}{2}[(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})]+[Re(\mathbf{y}_{S}^{T})-(\mathbf{a}_{N}-\mathbf{\hat{a}}_{N})^{T}\mathbf{K}_{NS}^{r}
](\mathbf{a}_{S}-\mathbf{\hat{a}}_{S})-\\\nonumber\epsilon<\mathbf{e}^{T}, (\mathbf{a}_{S}+\mathbf{\hat{a}}_{S})>,
\\
\left\{\begin{array}{ll}
0\leq [\mathbf{a}_{S}]_{i}([\hat{\mathbf{a}}_{S}]_{i})\leq C\tilde{R}(\xi_{i}^{r})(\tilde{R}(\hat{\xi}_{i}^{r})), i\in S\\
\xi_{i}^{r}(\hat{\xi}_{i}^{r})\geq 0, i\in S\\
\end{array}\right.
\label{subset optimization}
\end{IEEEeqnarray}
A proper work set selection strategy is required so that speed and performance requirement can be guaranteed. One idea is to perform update to dual variables that violate the complementary KKT conditions, which, based on (\ref{original KKT condition3}) in \ref{section lagrange duality}, can be formulated as 
\begin{IEEEeqnarray}[\relax]{l}
\left\{\begin{array}{ll}
(C\tilde{R}(\xi_{i}^{r})-\alpha_{i})\xi_{i}^{r}=0, i=1,2,\ldots, L\\
(C\tilde{R}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i})\hat{\xi}_{i}^{r}=0, i=1,2,\ldots, L\\
\alpha_{i}(\Re{(\mathbf{y}_{i})}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\epsilon-\xi_{i}^{r})=0, i=1,2,\ldots, L\\
\hat{\alpha}_{i}(-\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\Re{(\mathbf{y}_{i})}-\epsilon-\hat{\xi}_{i}^{r})=0, i=1,2,\ldots, L\\
\end{array}\right.
\label{complementary KKT condition1}
\end{IEEEeqnarray}
According to Osuna's theorem\cite{osuna1997improved}, the final convergence can be guaranteed. In SMO algorithm, heuristic methods are used to find a work set of size two in order to accelerate the decomposition process\cite{platt1999fast}. The heuristic method first searches among the non-bound variables (that is $0<\alpha_{i}<C\tilde{R}(\xi^{r}_{i})$ and $0<\hat{\alpha}_{i}<C\tilde{R}(\hat{\xi}_{i})$), which are more likely to violate the complementary KKT conditions, Then searching the whole dual variable set. The second dual variable that can maximize optimization step size is chosen. An approximate step size is used as evaluator for sake of reducing computational cost.

Another idea for work set selection is to choose the dual variables whose update can provide the maximum improvement to dual objective function. The improvement of the sub dual objective function is

@@

where $\Delta_{S}=\mathbf{a}_{S}^{new}-\mathbf{a}_{S}$, $\hat{\Delta}_{S}=\hat{\mathbf{a}}_{S}^{new}-\hat{\mathbf{a}}_{S}$, $\mathbf{a}^{new}_{S}$ and $\hat{\mathbf{a}}^{new}_{S}$ are the updates of $\mathbf{a}_{S}$ and $\hat{\mathbf{a}}_{S}$. $\bigtriangledown \theta_{S}^{r}$ in (\ref{maximum gain work set selection}),  based on (\ref{subset optimization}), can be written as

@@

\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}[(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+2(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})]+[\Re{(\mathbf{y}^{T}_{S})}-(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\\\nonumber\Re{(\mathbf{K})}_{NS}](\Delta_{S}-\hat{\Delta}_{S})-\epsilon\mathbf{e}^{T}_{S}(\Delta_{S}+\hat{\Delta}_{S})=-\frac{1}{2}(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+\{\Re{(\mathbf{y}^{T}_{S})}-[(\mathbf{a}_{S}-\hat{\mathbf{a}}_{S})^{T}\\
\Re{(\mathbf{K})}_{SS}+(\mathbf{a}_{N}-\hat{\mathbf{a}}_{N})^{T}\Re{(\mathbf{K})}_{NS}]\}(\Delta_{S}-\hat{\Delta}_{S})

@@

where we have 

@@

where $\Re{(\mathbf{K})}_{S}\in \mathbb{R}^{N_{r}\times S}$ denotes the matrix constructed by all the columns corresponding to the work set $S$. Therefore, (\ref{gain work set selection1}) can be rewritten as

@@

\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}(\Delta_{S}-\hat{\Delta}_{S})^{T}\Re{(\mathbf{K})}_{SS}(\Delta_{S}-\hat{\Delta}_{S})+[\Re{(\mathbf{y}^{T}_{S})}-(\mathbf{a}-\hat{\mathbf{a}})^{T}\Re{(\mathbf{K})}_{S}]
(\Delta_{S}-\hat{\Delta}_{S})
-\epsilon\mathbf{e}^{T}_{S}\\
(\Delta_{S}+\hat{\Delta}_{S}),
\label{gain of work set selection1 inter}
define intermediate variable vector $\Phi\in \mathbb{C}^{N_{r}}$, $\Re{(\Phi)}=\Re{(\mathbf{y})}-\Re{(\mathbf{K})}(\mathbf{a}-\hat{\mathbf{a}})$ and $\Im{(\Phi)}=\Im{(\mathbf{y})}-\Re{(\mathbf{K})}(\mathbf{b}-\hat{\mathbf{b}})$, let $\Phi_{S}$ denote the vector that consists of the components in $\Phi$ that corresponding to $S$.
Thus (\ref{gain of work set selection1 inter}) can be rewritten as 
\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}(\Delta_{S}-\hat{\Delta})^{T}_{S}\Re{(\mathbf{K})}_{SS}(\Delta-\hat{\Delta})_{S}+(\Re{(\Phi)}_{S})^{T}(\Delta-\hat{\Delta})_{S}-\epsilon\mathbf{e}^{T}_{S}\\
(\Delta+\hat{\Delta})_{S}

@@

(C\tilde{R}(\xi_{i}^{r})-\alpha_{i})\xi_{i}^{r}=0, i=1,2,\ldots, N_{r}\\

@@

(C\tilde{R}(\hat{\xi}_{i}^{r})-\hat{\alpha}_{i})\hat{\xi}_{i}^{r}=0, i=1,2,\ldots, N_{r}\\

@@

\alpha_{i}(\Re{(\mathbf{y}_{i})}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\epsilon-\xi_{i}^{r})=0, i=1,2,\ldots, N_{r}\\

@@

\hat{\alpha}_{i}(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\Re{(\mathbf{y}_{i})}-\epsilon-\hat{\xi}_{i}^{r})=0, i=1,2,\ldots, N_{r}

@@

Recall the discussions of slack variables by (\ref{definition of slack variable1}) and (\ref{definition of slack variable2}) in section \ref{section lagrange duality}. we have $\xi^{r}_{i}\hat{\xi}^{r}_{i}=0$. 
similar to the definitions in (\ref{definition of slack variable3}), we have
\xi^{r}_{i}(\hat{\xi}_{i}^{r})=|\Re{(\mathbf{y}_{i})}-\Re{(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}})}|_{\epsilon},
\label{definition of complex slack variables}
 therefore in (\ref{KKT complementary3}) and (\ref{KKT complementary4}), there is at least one of $(\Re{(\mathbf{y}_{i})}-<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\epsilon-\xi_{i}^{r})$ and  $(<\mathbf{h}_{i},\mathbf{w}>_{\mathbb{H}}-\Re{(\mathbf{y}_{i})}-\epsilon-\hat{\xi}_{i}^{r})$ can be non zero, therefore in order to satisfy equalities (\ref{KKT complementary3}) and (\ref{KKT complementary4}), at least one of $\alpha_{i}$ and $\hat{\alpha}_{i}$ need to be zero, that is $\alpha_{i}\hat{\alpha}_{i}=0$.

 Hence we can substitute $\lambda_{i}=\alpha_{i}-\hat{\alpha}_{i}$ and $|\lambda_{i}|=\alpha_{i}+\hat{\alpha}_{i}$, therefore the update unit is changed to the single optimization variable $\lambda_{i}$ rather than the pair $\alpha_{i}$ and $\hat{\alpha}_{i}$.

@@

\begin{IEEEeqnarray}[\relax]{l}
\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}\Sigma^{T}_{S}\Re{(\mathbf{K})}_{SS}\Sigma_{S}+(\Phi^{r}_{S})^{T}\Sigma_{S}-\epsilon<\mathbf{e}^{T}_{S},|\Lambda^{new}_{S}|-|\Lambda_{S}|>,
\label{gain work set selection lambda}
\end{IEEEeqnarray} 
In 1-D solver, $|S|=1$, based on (\ref{gain work set selection lambda}), the sub dual objective function corresponding to $\lambda_{m}$, $m=1,2,\ldots, N_{r}$ can be written as
\begin{IEEEeqnarray}[\relax]{l}
 \max_{\lambda_{m}}\quad \theta_{m}^{r}=-\frac{1}{2}(\lambda_{m}^{new})^{2}\Re{(\mathbf{K})}_{mm}
+[\Re{(\mathbf{y}_{m})}-\sum_{j\neq m}^{N_{r}}\Re{(\mathbf{K})}_{mj}\lambda_{j}]\lambda_{m}^{new}-\epsilon(|\lambda^{new}_{m}|),
 \label{optimization function 1-D}
 \end{IEEEeqnarray}
 Based on the definition of $\Phi$ in (\ref{gain work set selection2}), $\Re{(\Phi)}_{i}=\Re{(\mathbf{y}_{i})}-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\Re{(\mathbf{K})}_{ij}$, similarly, as to dual variable $\lambda^{i}_{i}$, $\Re{(\Phi)}_{i}^{i}=Im(y_{i})-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Re{(\mathbf{K})}_{ij}$. Thereafter, for sake of brevity, we use $\lambda_{i}$ instead of $\lambda_{i}^{r}$.
Take the partial derivative of $\theta_{m}^{r}$ respect to $\tilde{\lambda}^{new}_{m}$,  we have 
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
\frac{\partial \theta_{m}^{r}}{\partial \tilde{\lambda}^{new}_{m}}=-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}+\Re{(\mathbf{y}_{m})}-\sum_{j\neq m}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{mj}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))=\\
\nonumber
-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}+\Re{(\Phi)}_{m}+\lambda_{m}\Re{(\mathbf{K})}_{mm}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))\\
\Rightarrow \tilde{\lambda}_{m}^{new}=\lambda_{m}+\frac{\Re{(\Phi)}_{m}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))}{\Re{(\mathbf{K})}_{mm}},
\label{partial optimization function 1-D lambda}
\end{IEEEeqnarray} 
 The update of $\lambda_{m}$ is completed by clipping
\begin{IEEEeqnarray}[\relax]{l}
\lambda^{new}_{m}=[\tilde{\lambda}^{new}_{m}]^{CR^{'}(\xi_{m})}_{-CR^{'}(\xi_{m})}
\label{clipped new dual variable}
\end{IEEEeqnarray}

@@

based on (\ref{gain work set selection lambda}), The maximal gain of objective function with respect to the $m$th optimization variable $\lambda_{m}$ is 

@@

In 1-D searching procedure, the optimization variable whose update can achieve the maximum gain of sub dual objective function is chosen, assume the $k$th optimization variable is chosen, based on the this principle 

@@

k=\arg\max_{(m=1,2,\ldots, N_{r})} \bigtriangledown \theta_{m}^{r}.

@@

R(u)=\frac{1}{2}u^{2},
